%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

\cventry
{Research Engineer}
{Inria GraphIK}
{Montpellier, France}
{Sep. 2018 - Sep. 2019}
{
\begin{cvitems}
\item Developed a Maven library and Java application to process votes in CSV format and implemented several social choice algorithms.
\item Performed research on social choice and defeasible logic to write my MSc. thesis for the University of Buenos Aires.
\item Programming languages and frameworks: Java.
% \item Directors: Madalina Croitoru and Pierre Bisquert.
\end{cvitems}
}  
%---------------------------------------------------------

\cventry
{Software Engineer}
{Dubbing.digital}
{Buenos Aires, Argentina}
{Jan. 2018 - Sep. 2018}
{
\begin{cvitems}
\item Mobile application and front-end Web developer for Dubbing.digital.
% \item Implemented Apache Cordova notepad application for dubbing actors and producers and Front-end of a web application for business management as part of a 2-person team.
\item Implemented mobile notepad application and Front-end of a web application for business management as part of a 2-person team.
\item Programming languages and frameworks: Javascript, Node.js, Angular, CouchDB and Web-Standard (HTML, CSS).
\end{cvitems}
} 
%---------------------------------------------------------

\cventry
{Software Engineer}
{Despegar.com}
{Buenos Aires, Argentina}
{Oct. 2013 - Nov. 2014}
{
\begin{cvitems}
\item iOS Software Engineer for Despegar.com and Decolar.com, Latin America's leading travel company. 
\item Co-developed flight, hotel and package selling features for the iPhone and iPad platforms in a team of 15 people. 
\item Programming languages and frameworks: Objective-C and Swift.
\end{cvitems}
} 
%---------------------------------------------------------
\end{cventries}
