%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Martin Jedwabny <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-emerald}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[circle,noedge,left]{./src/profile}
\name{Martin}{Jedwabny}
\position{Computer scientist{\enskip\cdotp\enskip}Software Engineer}
\address{4 Rue Saint Louis, Bat. B, Apt. 8, 34000, Montpellier, France}

\mobile{(+33) 6-0563-8406}
\email{martinjedwabny@gmail.com}
\github{martinjedwabny}
\linkedin{martinjedwabny}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra informations}

% \quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
 {}
 {}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Motivation letter}
% How the letter is opened
\letteropening{To whom it may concern,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
% \letterenclosure[Attached]{}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Martin Jedwabny~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
% \makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

  Dear Rafał Mantiuk,

  I am writing to apply for the PhD Studentship in Machine Learning for Computer Graphics.
  
  About myself, my name is Martin Jedwabny, I am a computer science student from Universidad de Buenos Aires, Argentina.

  I read the information you provided at your website and went as far as I could go with the papers you mentioned and 
  I believe this is could be an excellent opportunity.

  Having studied Computer Science at the University of Buenos Aires (6-year degree, equivalent to MSc. + BSc.), 
  I had an excellent academic record and I developed a great interest in research, particularly in machine learning, algorithms and logics.
  
  At the same time, I pushed myself into working full time as a software engineer as well as being Teaching Assistant at my university. 
  I have plenty of experience in the industry developing high quality software and teaching skills I developed in my time as an assistant.
  
  Currently, I am working at the GraphIK group in Montpellier, France, for a one year MSc. thesis internship funded by the EU project NoAW and
  working under the supervision of Madalina Croitoru and Pierre Bisquert in the topics of voting, preference aggregation, argumentation,
  logics and knowledge base reasoning, in order to finish my degree's thesis (around July or August). You can of course contact them for references.
  
  During the internship, I acquired an enormous set of skills for doing research under the guidance of my supervisors.
  Reading papers efficiently, organization, academic writing, I believe these are skills you will find useful.
  After a few months, we got a demonstration paper accepted at the AAMAS conference, one of the most important
  Multi Agent System conference. We are also on the way of doing further conference submissions.
  
  On parallel and during my time at the university, I implemented numerous projects with popular ML frameworks
  (Scikit Learn, Tensor flow) and acquired a considerable amount of experience in Machine Learning and Data Science.
  Though my experience in Computer graphics is not as great as in other areas, I do think I could adapt easily
  and read whatever amount of research in order to prepare for this opportunity, it is well worth it. Moreover, I do 
  think my knowledge in ML is more than adequate.
  
  After completing the PhD, I plan to pursue further academic positions as it is my passion and quite frankly the only thing I am interested in doing in my future.

\end{cvletter}

%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
